Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2025-04-04 paper/paper.tex
author info, AFOSR grant acknowledgment

% -*- fill-column: 80; -*-
%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
% For final camera-ready submission, w/ required CCS and ACM Reference
\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\author{Max S. New}
\affiliation{
  \department{Electrical Engineering and Computer Science}
  \institution{University of Michigan}
  \country{USA}
}
\email{maxsnew@umich.edu}
\orcid{0000-0001-8141-195X}

@@

@@

\begin{acks}
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}. This work is also supported by
  the ERC Consolidator Grant BLAST and the ARIA programme on Safeguarded AI.
  Any opinions, findings, and conclusions or recommendations expressed in 
  this material are those of the author and do not necessarily reflect the 
  views of the National Science Foundation, the European Research Council or
  the Advanced Research and Invention Agency.
\end{acks}

>>>>

% -*- fill-column: 80; -*-
%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For final camera-ready submission, w/ required CCS and ACM Reference
\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\author{Max S. New}
%% \authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0001-8141-195X}
\affiliation{
  \position{Assistant Professor}
  \department{Computer Science and Engineering}              %% \department is recommended
  \institution{University of Michigan}            %% \institution is required
  % \streetaddress{2260 Hayward St.}
  \city{Ann Arbor}
  \state{MI}
  % \postcode{48109-2121}
  \country{USA}                    %% \country is recommended
}
\email{maxsnew@umich.edu} %% \email is recommended

@@

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

@@

\begin{acks}
  This material is based upon work supported by the Air Force Office of
  Scientific Research under Grant No.~\grantnum{}{FA9550-23-1-0760}.  Any
  opinions, findings and conclusions or recommendations expressed in this
  material are those of the authors and do not necessarily reflect the views of
  the U.S. Department of Defense.
  %
  This work is also supported by the ERC Consolidator Grant BLAST and the ARIA
  programme on Safeguarded AI.  Any opinions, findings, and conclusions or
  recommendations expressed in this material are those of the author and do not
  necessarily reflect the views of the National Science Foundation, the European
  Research Council or the Advanced Research and Invention Agency.
\end{acks}
